Citation Analysis of Computer Science

### 2019-11-15 Scientometrics/comp.tex
Edited the full text data search section

\emph{Data} The dblp computer science bibliography consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz from  `https://dblp.uni-trier.de/xml/'. Publications were parsed from the xml source file and loaded into a PostgreSQL database. We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of the construction of a larger data platform for research evaluation~\cite{Korobskiy_2019}. Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles. The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions. The ts\_vector is then matched with DBLP document titles. A ts\_rank is returned based on the frequency of matching lexemes. Only records in dblp with DOIs (4,291,130) were considered and only matches with a rank of $>$ 0.99 were accepted. This procedure resulted in a dataset of 634,100 publications with Scopus identifiers. Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset. This dataset was labelled \emph{comp}.\par

>>>>

\emph{Data} The dblp computer science bibliography consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz from  `https://dblp.uni-trier.de/xml/'. Publications were parsed from the xml source file and loaded into a PostgreSQL database. We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of the construction of a larger data platform for research evaluation~\cite{Korobskiy_2019}. Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles. The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a text search vector which lists the lexemes. The vectors are then matched with corresponding text search vectors extracted from DBLP document titles. A rank is returned based on the frequency of matching lexemes. Only records in dblp with DOIs (4,291,130) were considered and only matches with a Postgres ts\_rank of $>$ 0.99 were accepted. This procedure resulted in a dataset of 634,100 publications with Scopus identifiers. Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset. This dataset was labelled \emph{comp}.\par
